### 2019-02-02 Seneca.tex
chandras pass

Seneca automatically builds and deploys a AWS Lambda application
from the machine learning application specified.
To do so, Seneca launches a docker container that mirrors the
AWS Lambda execution environment, checks and installs
the machine learning application and any libraries it requires,
and compresses the application and uploads it to S3 (avoiding
the AWS Lambda handler size restriction of 10MB).
Seneca constructs an AWS Lambda handler from a template
that when executed will download and uncompress the application,
download the dataset and split it into a training and testing set,
and construct, test, and evaluate a model using the application
and a set of hyperparameter values passed in by Seneca as arguments.
The handler returns a testing score.
Upon completion of this process, the container deploys the handler
to AWS Lambda using the
AWS Command line Interface~\cite{ref:awscli}.

@@

For current function invocation, Seneca integrates 
Celery~\cite{ref:celery}. Celery is an asynchronous task queue 
that uses distributed message passing. Celery workers are processes 
that take tasks from the queue, execute tasks, and store the
result in a database (we use Redis~\cite{ref:redis} in our prototype).

Based on the configuration file, Seneca creates a list of 
payloads (function arguments) that contains values of 
hyperparameters.  The complete list contains all combinations of parameter
settings.  Seneca places the list on the queue and celery 
workers invoke the Lambda handler of the application, passing in the
payload to the handler to use for model construction.  Upon function
termination, the work records the evaluation score (and serialized model)
in the database with the hyperparameter configuration from the payload.
When the queue is drained and all workers have completed, Seneca
extracts and reports the best score and configuration from the database.

>>>>

Seneca automatically builds and deploys a AWS Lambda application
from the machine learning application specified.
To do so, Seneca launches a docker container that mirrors the
AWS Lambda execution environment, checks and installs
the machine learning application and any libraries it requires,
and compresses the application and uploads it to S3 (avoiding
the AWS Lambda handler size restriction of 10MB).
Seneca constructs an AWS Lambda handler from a template
that when executed will download and uncompress the application,
download the dataset and split it into a training and testing set,
and construct, test, and evaluate a model using the application
and a set of hyperparameter values passed in by Seneca as arguments.
Users can specify the train/test split that should be used by Seneca; the
default is 80\%/20\% for classification tasks.
The handler returns a testing score. 
Upon completion of this process, the container deploys the handler
to AWS Lambda using the
AWS Command line Interface~\cite{ref:awscli}.

@@

For parallel function invocation, Seneca integrates 
Celery~\cite{ref:celery}. Celery is an asynchronous task queue 
that uses distributed message passing. Celery workers are processes 
that take tasks from the queue, execute the tasks with the auguments specified, 
and store the result that is returned 
in a database (we use Redis~\cite{ref:redis} in our prototype).

Based on the configuration file, Seneca creates a list of 
payloads (function arguments) that contains values of 
hyperparameters.  The complete list contains all combinations of the
specified parameter
settings.  Seneca places the list on the queue and celery 
workers invoke the Lambda handler of the application, passing in the
payload (hyperparameter values) to the handler to use for model construction.  
Upon function
termination, the work records the evaluation score (and serialized model)
in the database with the hyperparameter configuration from the payload.
When the queue is drained and all workers have completed, Seneca
extracts and reports the best score, configuration, and model from the database.
Users can then evaluate the prediction power of the models (using Seneca if desired) 
for other datasets (to amortize the time/cost of Seneca) without retraining.

We assume that the dataset supplied to Seneca by the user
is representative of datasets on which the 
resulting model will be use.  In addition, we use prediction error as the 
score (i.e., mean squared error for regression and accuracy percentage for classification) 
instead of $R^2$, which describes explanatory power, to avoid overfitting.
As part of future work, we are considering using multiple datasets and a ranges
of hyperparameter values (versus lists) to preclude the need for users to specify
them and to consider a wider range of possible values.

### 2019-02-02 intro.tex
chandras pass

In this work, we investigate the efficacy of using AWS Lambda
for tuning machine learning applications.
To date, Lambda has not be heavily used for training and evaluating
machine learning models because of a concern that 
doing so will result in high overhead (i.e. be costly) because
of the stateless nature of serverless functions~\cite{ref:onesteptwostep}.
At the same time, identifying the ``best'' configuration for advanced
machine learning models is challenging given the large number of configuration
options, i.e., hyperparameters, typical of models today.
Hyperparameters governs the learning process of machine learning applications.
Given that parameter sweeps are embarrassingly parallel, we believe
that such tuning is a good fit for the serverless model.
To investigate this potential, its overhead, and to simplify the 
use of Lambda for training, testing, and evaluation machine learning models, 
we design and develop a new system and toolset called \textit{Seneca}.

Specifically, Seneca implements, packages, and deploys 
machine learning applications as stateless functions to AWS Lambda.
It then orchestrates exhaustive evaluation of hyperparameter settings
to identify the best performing model (for a given dataset) by
comparing the error and accuracy across models.  Users present
Seneca with their application, a range of values for 
each hyperparameter (or the default can be used), and a dataset.
Seneca produces, tests, and evaluates models for all combinations 
of hyperparameters and returns to the user, 
the set of parameters (or the model itself) that produces
the best cross-validation score (e.g. lowest squared error or highest
accuracy).

We deploy Seneca on AWS Lambda and evaluate its tuning performance, cost,
and memory use for six machine learning applications and datasets. We 
find that Seneca is effective for quickly training these
models and identifying the best performing hyperparameter setting for 
these applications. We also find 
Seneca to be very low cost and able to automatically 
identify the 
best memory configuration for each application further lowering its 
by 10-30\%.
We intend to make Seneca and the applications available as open source
when/if this paper is accepted for publication.  In the sections
that follow, we overview our design and implementation of Seneca and then
present our empirical methodology and results.

>>>>

In this work, we investigate the efficacy of using AWS Lambda
for tuning machine learning applications.
To date, Lambda has not be heavily used for training and evaluating
machine learning models because of a concern that 
doing so will result in high overhead (i.e. be costly) because
of the stateless nature of serverless functions~\cite{ref:onesteptwostep}.
At the same time, identifying the ``best'' configuration for advanced
machine learning models is challenging given the large number of configuration
options, i.e., hyperparameters, typical of models today.
Hyperparameters govern the learning process of machine learning applications.
Given that parameter sweeps are embarrassingly parallel, we believe
that such tuning is a good fit for the serverless model.
To investigate this potential, its overhead, and to simplify the 
use of Lambda for training, testing, and evaluation machine learning models, 
we design and develop a new system and toolset called \textit{Seneca}.

Specifically, Seneca implements, packages, and deploys 
machine learning applications as stateless functions to AWS Lambda.
It then orchestrates exhaustive evaluation of hyperparameter settings
to identify the best performing model (for a given dataset) by
comparing the error and accuracy across models.  We consider
prediction accuracy (as opposed to explanatory power) as the
scoring metric (mean squared error for regression 
and accuracy percent for classification), to avoid overfitting.
Users present Seneca with their application, a range of values for 
each hyperparameter (or the default can be used), and a representative dataset.
Seneca produces, tests, and evaluates models for all combinations 
of hyperparameters and returns to the user
the set of parameters (or the model itself) that produces
the best cross-validation score (e.g. lowest squared error or highest
accuracy) for the dataset. Users can employ this model for other datasets
(with Seneca if desired) without retraining the model to amortize the cost
of Seneca further.

We deploy Seneca on AWS Lambda and evaluate its tuning performance, cost,
and memory use for six machine learning applications and datasets. We 
find that Seneca is effective for quickly training these
models and identifying the best performing hyperparameter setting for 
these applications. We also find 
Seneca to be very low cost and able to automatically 
identify the 
best memory configuration for each application further lowering its 
by 10-30\%.
As such, Seneca greatly simplifies model construction and comparison and 
does so with very low latency and at very low cost.
We intend to make Seneca and the applications available as open source
when/if this paper is accepted for publication.  In the sections
that follow, we overview our design and implementation of Seneca and then
present our empirical methodology and results.
